Efficient and Scalable Bipartite Matching with Fast Beta Linkage (fabl)

### 2023-07-20 ba_resubmit/rebuttal/response.tex

\begin{document}

	% ****************** TITLE ****************************************

	\title{Response to Reviewer Comments}
	\maketitle

\textcolor{teal}{We thank the Editor and reviewers for their assessment and constructive feedback.}

%Thank you for the thoughtful feedback. We have made several broad changes to address the Editor's and Associate Editor's overall critiques, and have addressed each specific comment from the reviewer.

@@

\section{AE Comments}

\pointRaised{AE}{I must add that reading the paper still feels like a chore, in part because the notation is so heavy, which may be hard to avoid, but also, in part, because some wording choices make certain sentences hard to parse, which can certainly be improved.}

\reply{
\textcolor{teal}{Thank you for the opportunity to submit a revision. 
We have provided detailed responses to the reviewers' comments below, 
which prompted significant changes in our article. Specifically, we have attempted to improve notation and wording choices, at the reviewers' suggestion. 
}
}

%We propose fast beta linkage (\texttt{fabl}), which extends the \texttt{BRL} model for increased efficiency and scalability. We use independent priors for the matching status of each record, inducing a dependency that is stronger than the record pair independence in the original \cite{fellegi_theory_1969} but weaker that the one-to-one requirement of \cite{sadinle_bayesian_2017}. This independence assumption allows for a scalable update of the Gibbs sampler, contrasting sequential updates of \cite{sadinle_bayesian_2017}. We employ the decision theoretic  technique of \cite{sadinle_bayesian_2017} in order to ensure our method after record linkage is bipartite. This discovery allows us to (1) employ hashing techniques that speed up calculations and reduce computational costs, (2) compute the pairwise record comparisons over large data files via parallel computing, and (3) reduce memory costs via a novel method, storage efficient indexing. These contributions allow \texttt{fabl} to perform record linkage on much larger data files than previous Bayesian Fellegi-Sunter models at significantly increased speed with similar levels of accuracy. In particular, computation time under \texttt{BRL} grows quadratically, with the size of each data file, while computation time under \texttt{fabl} grows linearly, only with the size of the smaller data file. Finally, we provide two real illustrations of our methodology and simulation studies with reproducible software.

%}

@@

\pointRaised{AE}{Line 80 on p. 3 says: “For ease of readability, we follow the convention established by \cite{sadinle_bayesian_2017} and say “record $i \in X_1$” rather than the more compact $x_{1i}$.” Taking this at face value implies that, in any sentence, one could swap “record $i \in X_1$” for “$x_{1i}$,” which clearly is not true.  So, as it stands, the sentence does little to improve ease of readability.  In fact, if the point is that “$x_{1i}$” will never be used again, why is the notation introduced in the first place?}

%%% RCS: Thank the Editor, explain the change. I have removed repetition and shortened this bit.

\reply{
Thank you for the suggestion. We now refer to the two data files as
 $A$ and $B$, where the updated material reads:

@@

\setcounter{responsectr}{0}
\section{Reviewer Comments}

	\pointRaised{R}{%
	For the missing data treatment now included just before Section 2.1, is the assumption truly missing at random, or missing completely at random? Or, does this distinction not matter because of the independence assumed across elements of the comparison vector?}

	\reply{\textcolor{teal}{The distinction does not matter due to assuming that the comparison vectors are conditionally independent given the coreference matrix (or matching label). We now state the following in Section 3, page 5:}

	\textcolor{teal}{``Assume the comparison vectors are conditionally independent given the coreference matrix (or matching label) and that missing comparisons are  missing at random (MAR) or missing completely at random (MCAR). Due the the conditional independence assumption, we can marginalize over the missing data in (6a) and perform all computation using the observed data. For details, refer to \cite[Section 6.2]{LittleRubin2002}, \cite[Section 3.1]{sadinle_detecting_2014}, and \citep[Section 4.2]{sadinle_bayesian_2017}.}

@@

	\pointRaised{R}{%
	Appendix 8.2: I appreciate the streamlining of the discussion of the proposed algorithms and think it was a good choice to move the full derivation to an appendix. However, I do not follow the re-expression of the pmf for $\Gamma_{.j}$. First, the opening square brackets are still misplaced
	throughout. In the second line of this derivation, the authors divide the expression by a product of the element-wise conditional probabilities of a match in the comparison vector (u), raised by an indicator that the element of the comparison vector equals a particular value. Perhaps I misunderstand, but I believe this product is not constant in $\Gamma_{.j}$ or $u$, and so the total expression is not proportional to the line above, as interpreted as a pmf. I think that the end effect is that the last line of the newly expressed pmf is missing a factor of $\prod_i \prod_f \prod_l u_{fl}^{I(\gamma_{ij}^f = l) I_{obs}(\gamma_{ij}^f)}$ regardless of the value of $z_j$.}

%% Don't apologize. Just answer the questions very completely.

%\textcolor{teal}{Don't apologize!}

\reply{%
	The square brackets have been corrected. We have revised the derivation of the full conditional distribution of $Z_j$, separately handling the case when $B_j$ has a match and when it does not. Refer to Appendix A, pages 26 -- 27 regarding this extended derivation.
	}

@@

%\reply{%
%	The square brackets have been corrected, and we apologize for the oversight. We have clarified derivation of the likelihood for $Z_j$, separately handling the case when $B_j$ has a match and when it does not.
%}

	\pointRaised{R}{%
Appendix 8.2: Thank you for including the details on integrating out pi from the full conditionals. They surprised me. I had assumed that the authors had integrated out pi in the prior for Z, as this is what Sadinle (2017) had done to form the “beta prior for bipartite matchings”. (1) Does the alternate approach presented in this paper provide a different algorithm than directly integrating the prior distribution? (2) Is the presented alternative approach justified?}

\reply{No, in \text{fabl}, we do not integrate out $\pi$ as done in \cite{sadinle_bayesian_2017} because this leads to a sequential sampler.

(1) Yes, our alternative approach is different than directly integrating over the prior distribution $\pi.$ 
%We have attempted to make this more clear in our revised version. 
In short, our prior distribution over $Z$ leads to a Gibbs sampler that leads to parallel updates, which contrasts that of \cite{sadinle_bayesian_2017}. Of course, we could integrate out $\pi$ in our approach, however, this leads to sequential updates, which would be slow in practice. See Appendix A, page 27.

(2) Yes, our alternative approach is justified. We provide a justification in Appendix A, page 27 regarding why the updates are independent and not sequential. Thank you for the excellent questions, which have greatly improved our paper.

@@

%
%\reply{%
%	We realize that the integration of pi out of the full conditionals is not necessary for our sampler. For clarity, we decided to redo the simulations using a Gibbs sampler that samples $\pi$ from its full conditional, and then samples $Z$ from its full conditionals. We obtained equivalent results, which is unsurprising, because with high numbers of observations, the posterior of the beta distribution is highly concentrated around its mean.
%	
%	Therefore, we have updated the paper with full conditionals for the standard Gibbs sampler. We leave the remark about marginalization in the Appendix to facilitate comparisons to Sadinle's method.
%
%}

\pointRaised{R}{%
	I do not understand the statement just below Equation (10): “When j has no match in $X_1$, we write $(n_1 +j, j) \in h_{P+1}$” My understanding of these patterns is that they are based on observed comparison vectors without consideration of Z (matches). In the second paragraph of Section 4.3, the H notation includes the matches (Z), in notation and definition that seems to conflict with the statement just below Equation (10). This also comes into play in Equation (16)}

	%% RCS: Tried to answer this from the original paper and the updated paper. Tried to make it shorter and close it out very quickly.

	\reply{\textcolor{teal}{Yes, in the original manuscript, the comparison vectors are created and therefore, patterns are assigned) without regard to $Z$. Given the confusion, we have removed the sentence.	}}

@@

\pointRaised{R}{%
	Generally, the authors seem to arbitrarily use upper and lower case z interchangeably in function definitions.}

\reply{%
	We use $Z$ when discussing a random quantity, and $z$ to reference a realized value. We have revised all instances of the inconsistency. 
}

\pointRaised{R}{%
Equations (8) and (9): Should the weights have superscript (s) (as the Zs do)?}

\reply{%
	This has been fixed. \textcolor{teal}{Refer to equations (12) and (13), page 7.}
}

### 2023-07-20 ba_resubmit/kundinger_resubmit2.tex
update.

\textcolor{teal}{We now explain how we accommodate missing fields, which leads to missing comparison vectors. To denote a missing value in any $\gamma_{ij}^f$, we use $I_{obs}(\gamma_{ij}^f)=1$ when $\gamma_{ij}^f$ is observed and $I_{obs}(\gamma_{ij}^f)=0$ otherwise. Assume the comparison vectors are conditionally independent given the coreference matrix (or matching label) and that missing comparisons are  missing at random (MAR) or missing completely at random (MCAR). Due the the conditional independence assumption, we can marginalize over the missing data in (\ref{eqn:likelihood}) and perform all computation using the observed data. For details, refer to \cite[Section 6.2]{LittleRubin2002}, \cite[Section 3.1]{sadinle_detecting_2014}, and \citep[Section 4.2]{sadinle_bayesian_2017}.}

>>>>

\textcolor{teal}{We now explain how we accommodate missing fields, which leads to missing comparison vectors. To denote a missing value in any $\gamma_{ij}^f$, we use $I_{obs}(\gamma_{ij}^f)=1$ when $\gamma_{ij}^f$ is observed and $I_{obs}(\gamma_{ij}^f)=0$ otherwise. Assume the comparison vectors are conditionally independent given the coreference matrix (or matching label) and that missing comparisons are missing at random (MAR) or missing completely at random (MCAR). It is important to note that for likelihood based inference, both MAR and MCAR lead to ignorability, or rather, being able to consider the likelihood for the observed data \citep[Section 6.2]{LittleRubin2002}. Therefore, we can marginalize over the missing data in (\ref{eqn:likelihood}) and perform all computation using the observed data. For details, refer to \cite[Section 6.2]{LittleRubin2002}, \cite[Section 3.1]{sadinle_detecting_2014}, and \citep[Section 4.2]{sadinle_bayesian_2017}.
}

%Due the the conditional independence assumption, MAR or MCAR lead to the same treatment of the missing data. That is, for likelihood based inference both MAR and MCAR lead to ignorability, or rather, both lead to being able to consider just the likelihood for the observed data \citep[Section 6.2]{LittleRubin2002}.

%we can marginalize over the missing data in (\ref{eqn:likelihood}) and perform all computation using the observed data. For details, refer to \cite[Section 6.2]{LittleRubin2002}, \cite[Section 3.1]{sadinle_detecting_2014}, and \citep[Section 4.2]{sadinle_bayesian_2017}.}
